Thesis Title

### 2022-03-24 chapters/thesis_outline.tex
Updates from Overleaf

\textbf{Chapter 1} corresponds to the general introduction that highlights the impact of genomics in clinical microbiology, both in its diagnostic and surveillance prongs. This chapter further expands on this topic by expanding the concept of whole genome sequencing to metagenomics, both metataxonomics and shotgun, introducing the possibility of the identification and characterisation of a potential pathogen without the need for \textit{a priori} knowledge. In this chapter, the importance of bioinformatic analysis of these data is highlighted, showcasing its complexity and the major pitfalls, such as reproducibility and transparency of the results obtained. succinctly, the entire process in clinical microbiology for bacterial and viral infections is showcased through its different approaches: classical biochemical and molecular methods, whole genome sequencing, and sequencing through metagenomics, with a focus on the computational requirements necessary.

@@

\textbf{Chapter 3} consists in ...

>>>>

\textbf{Chapter 1} corresponds to the general introduction that highlights the impact of genomics in clinical microbiology, both in its diagnostic and surveillance prongs. This chapter further expands on this topic by expanding the concept of whole genome sequencing to metagenomics, both metataxonomics and shotgun, introducing the possibility of the identification and characterisation of a potential pathogen without the need for \textit{a priori} knowledge. In this chapter, the importance of bioinformatic analysis of these data is highlighted, showcasing its complexity and the major pitfalls, such as reproducibility and transparency of the results obtained. In summary, the entire process in clinical microbiology for bacterial and viral infections is showcased through its different approaches: classical biochemical and molecular methods, whole genome sequencing, and sequencing through metagenomics, with a focus on the computational requirements necessary.

@@

\textbf{Chapter 3} describes the ...
